\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-29 metatheory-condensed.tex
Update Sealing Example.

    (* s[@₄@] : {ty : 𝕎τ[@₁@]; ... subst : tm → nat → tm → tm } 
          | [ty : 𝕌; ... ; tm : 𝕌; subst : tm → nat → tm → tm] *)
    - o[@₄@] = μ+ o[@₃@] s[@₄@] .. : 𝕃{ty : 𝕎τ[@₁@]; ... t[@₁@] : tm}

    (* s[@₅@] : {ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst : 𝕃(RecSig); t1 : tm} 
          | [ty : 𝕌; tm : 𝕌; subst : 𝕃(RecSig); t1 : tm] *)
    - o[@₅@] = μ+ o[@₄@] s[@₅@] : 𝕃{ ... }
  \end{lstlisting}

@@

Basically, the hidden prior fields---inductive type are sealed into arbitrary type with ``constructors only'', where the recursion is constructed without sealing the inductive type.  Generally speaking, each extensible inductive type are hidden for all the other fields except for the recursion on itself. Furthermore, normal fields (e.g. "t1, t2") can expose its definition to all other fields in meta-theory by using singleton type. (e.g.  using "t1 : S(tvar 0)" instead of the current "t1 : tm"); and then overridable fields are hidden for normal fields (by sealing "t1 : S(tvar 0)" into "t1 : tm"). Generally speaking, anything with explicit "hiding" decoration can be understood as sealing.

>>>>

    (* s[@₄@] : {ty : 𝕎τ[@₁@]; ... subst : tm → nat → tm → tm } 
          | [.. ; tm : 𝕌; tvar : nat → tm; .. subst : tm → nat → tm → tm] *)
    - o[@₄@] = μ+ o[@₃@] s[@₄@] [@("tvar"~0)@] : 𝕃{ty : 𝕎τ[@₁@]; ... t[@₁@] : [@\TyS{"tvar"~0}@]}

    (* s[@₅@] : {ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]} 
          | [ty : 𝕌; tm : 𝕌; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]] *)
    - o[@₅@] = μ+ o[@₄@] s[@₅@] .. : 𝕃{ ... }
  \end{lstlisting}

@@

Basically, the hidden prior fields---inductive type are sealed into arbitrary type with ``constructors only'', where the recursion is constructed without sealing the inductive type.  Generally speaking, each extensible inductive type are hidden for all the other fields except for the recursion on itself.

We choose to expose the definition of $t_1$ to all the following fields including $t_2$ by using singleton type $\TyS{-}$. If other fields, say $t_3$, want to hide it, just seal $t_1$ into type "tm"; and then overriding $t_1$ will not disrupt the inheritablity of $t_3$. But such overriding will definitely disrupt the inheritablity of $t_2$ as $s_5$ doesn't hide $t_1$. Generally speaking, any field that has a clear "hiding" semantic on the prior fields can be understood as sealing. All of our plugin commands have clear "hiding" semantics.
